\documentclass{article}
\begin{document}
\section*{SE PROJECT GROUP 2}
\subsection*{PROJECT ONE}
\section*{A management system for a speciality clinic}

\subsection*{Project Description}

For our project, we have a small clinic with 5 dentists. We are designing an interactive system where patients can interact with the clinic via a website where they can register (first time visitors) and get details for signing in later before the appointment to fill in required forms, and where already registered patients can sign in, make appointments and also check and update their personal details or any other changes if there need be.

\subsection*{Brief Plan}

We have two parts to it, the front end and the back end. The front end is about creating visual elements of the system, the start or homepage that is displayed to our patients when they visit the webpage. We will be using HTML, CSS and Javascript for this.
On this startup page we plan on having a brief clinic description on what kind of services the clinic offers and sign up and sign in prompts.(Darlington Manhema and Timukudzei Mapurisa's tasks)\\\\
The back end is where we monitor functionality of the site and make it responsive to user input. This is where we will create a database (using MySQL) to hold all the patient information, history, appointments, dentists details and also update it all in the event of changes. This part is where we will link the database to the browser. we will be using a php file for linking and also python if it becomes necessary.(Faith Mangwiro and Sibongile Mahlake's tasks)

\subsection*{Inputs and Outputs expected}

Upon registration, patients provides the following:\\\\
-First name\\
-Surname\\
-Initial\\
-Date of birth\\
-Email address\\
-Cellphone number\\
-Insurance scheme and who is responsible for it\\
-Details of primary person insured\\\\

Output expected\\\\
-Patient ID\\
-password\\\\

These will be used as credentials to sign in as a member to provide more information and fill in the provided form. 









	
	
\end{document}